SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-12-23 maintex.tex
more text edits to sections 2-3

@@

\begin{equation}\label{eq:blue}
NUV-r = 3.1682 - 0.16 (\mathcal{M}_{\rm i}+18)
\end{equation}
\begin{equation}\label{eq:red}
NUV-r = 4.7866 - 0.04 (\mathcal{M}_{\rm i}+18),
\end{equation}
Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the $i$-band magnitude from the NSA catalog. We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}. Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers. Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.

@@

To select paired galaxies out of our object catalog, we inspect the spectra of each object. We use our own {\sc idl} based spectral fitting code, {\sc spfit}, to model the spectra from the MaNGA datacubes. {\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citepalias{Fu:2018}. Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).

@@

For each MaNGA 1\arcsec$\times$1\arcsec\ spaxel, we use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.

We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination.

@@

@@

\begin{deluxetable*}{cccccccccc}
%\tablestypesize{\small} \tablewidth{0pt}
\tablecaption{Pair Catalog}
\tablehead{
\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
}
\decimals
\startdata
7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
\enddata
\end{deluxetable*}

>>>>

\subsection{\textbf{Emission Line Extraction}}\label{sec:spfit}

\textbf{
We use our own {\sc idl} based spectral fitting code, {\sc spfit}\footnote{\url{https://github.com/fuhaiastro/spfit}}, to model the spectra from the MaNGA datacubes. {\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citepalias{Fu:2018}. Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD). The code used the SSP templates from the MUISCAT library \citep{Vazdekis:2012} which allows a spectral range of 3465$-$9469 \AA\ with a uniform spectral resolution of FWHM $=$ 2.5 \AA.
}

\textbf{
For each MaNGA 1\arcsec$\times$1\arcsec\ spaxel, we use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
}

MaNGA DAP \citep{Belfiore:2019}, Pipe3D \citep{Sanchez:2016a, Sanchez:2016b}

\subsection{\textbf{Selecting Star Forming Galaxies}}\label{sec:sf}

@@

\begin{equation}\label{eq:blue}
NUV-r = 3.1682 - 0.16 (\mathcal{M}_{\rm i}+18)
\end{equation}
\begin{equation}\label{eq:red}
NUV-r = 4.7866 - 0.04 (\mathcal{M}_{\rm i}+18),
\end{equation}
Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the $i$-band magnitude from the NSA catalog. We further apply an \ewha\ $\ge$ \textbf{6\AA} cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}. \textbf{This effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in the centers of our galaxies.} Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers. Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch. \textbf{}

@@

To select paired galaxies out of our object catalog, we inspect the spectra of each object.

@@

We correct the emission lines extracted by {\sc spfit} for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination. \textbf{To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ewha_comb.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_prof} but for EW(H$\alpha$). }
\label{fig:ewha_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{deluxetable*}{cccccccccc}
%\tablestypesize{\small} \tablewidth{0pt}
\tablecaption{Pair Catalog}
\tablehead{
\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
}
\decimals
\startdata
7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
\enddata
\tablecomments{
(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10) stellar mass. \\ \\
(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
}
\end{deluxetable*}
